---
title: "Using Tidy FFT"
subtitle: "Analyze Time Series data with tidy_fft"
author: "Steven P. Sanderson II, MPH"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Using Tidy FFT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(healthyR.ts)
```

# Introduction

In this vignette we will discuss how to use the `tidy_fft` function, what it does,
and what it produces.

# The Function

The `tidy_fft` function has only a few parameters, six to be exact. There are some
sensible defaults made. It is important that when you use this function, that you
supply it with a full time-series data set, one that has no missing data in it as
this will affect your results.

## Funcation and Parameters

The function and its full parameters are as follows:

```r
tidy_fft(
  .data,
  .date_col,
  .value_col,
  .frequency = 12L,
  .harmonics = 1L,
  .upsampling = 10L
)
```
The `.data` argument is the actual formatted data that will get passed to the function,
the timeseries data. The `.date_col` argument is the column that holds the datetime
of interest. The `.value` column is the colmn that holds the value that is being
analyzed by the function, this can be counts, averages, any type of value that is
in the timeseries.
